---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r knitrsetup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

```{r mainexample, echo = FALSE}
suppressMessages(suppressWarnings(library(dirq)))
```

# dirq - A Filesystem Directory Based Queue

A port of Perl module [Directory::Queue::Simple]
  (http://search.cpan.org/dist/Directory-Queue/)
The goal of this package is to offer a simple queue system
using the underlying filesystem for storage, security and
to prevent race conditions via atomic operations.

A simple producer:

```{r producer}
path <- tempfile() # Define a path to your queue.
path # In real life, temp files go away when the session exits, so be careful.
q <- dirq(path) # Create a new queue or recover an existing one.
for (i in seq.int(1, 100)) {
  name <- q$add(list(data = paste("element", i)), mode = "json")
  cat(name)
}
```

A simple consumer:

```{r consumer}
q <- dirq(path)
cursor <- q$first()
while (!is.null(cursor)) {
  if (q$lock(cursor)) {
    cat(paste("reading element", cursor$name))
    data <- q$get(cursor, mode = "json")
    q$remove(cursor)
    # or use q$unlock(cursor) to just peek at data
  }
  cursor <- q$next()
}
```

# Similar work

## txtq

[Will Landau](https://github.com/wlandau)'s [`txtq`](https://github.com/wlandau/txtq) is also a pure filesystem-based queue.

## liteq

[Gábor Csárdi](https://github.com/gaborcsardi)'s [`liteq`](https://github.com/r-lib/liteq) package offers essentially the same functionality implemented with SQLite. It has a some additional features, such as the ability to detect crashed workers and re-queue failed messages, but it was in an early stage of development at the time `dirq` was released.

## Other message queues

There is a plethora of message queues beyond R, most notably [ZeroMQ](https://zeromq.org) and [RabbitMQ](https://www.rabbitmq.com/). In fact, [Jeroen Ooms](https://github.com/jeroen) and [Whit Armstrong](https://github.com/armstrtw) maintain [`rzmq`](https://github.com/ropensci/rzmq), a package to work with [ZeroMQ](https://zeromq.org) from R. Even in this landscape, `dirq` has advantages.

1. The `dirq` user interface is friendly, and its internals are simple. No prior knowledge of sockets or message-passing is required.
2. `dirq` is lightweight, R-focused, and easy to install. It only depends on R and a few packages on [CRAN](https://cran.r-project.org).
3. Because `dirq` it is file-based,
    - The queue persists even if your work crashes, so you can diagnose failures with `q$log()` and `q$list()`.
    - Job monitoring is easy. Just open another R session and call `q$list()` while your work is running.
